\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-07 doc/paper.tex
for to -> to

We presented \fs, a Mathematica package, which generates fast and
modular spectrum generators for non-minimal SUSY models.  It comes
with plenty of predefined models for the CMSSM, NMSSM, USSM, \ESSM,
MRSSM etc., which can be generated immediately without any editing.  In particular the CMSSM
and NMSSM spectrum generators constitute alternatives for to the
existing ones Softsusy, SPheno and NMSPEC.  We have shown that the
generated source code can be influenced at two different levels: The
\mathematica level where the user provides a model file, and the C++
level where the generated objects can be easily exchanged, extended,
modified and reused.  This provides great flexibility for creating
custom spectrum generators for both the most common and most
extraordinary models.

>>>>

We presented \fs, a Mathematica package, which generates fast and
modular spectrum generators for non-minimal SUSY models.  It comes
with plenty of predefined models for the CMSSM, NMSSM, USSM, \ESSM,
MRSSM etc., which can be generated immediately without any editing.
In particular the CMSSM and NMSSM spectrum generators constitute
alternatives to the existing ones Softsusy, SPheno and NMSPEC.  We
have shown that the generated source code can be influenced at two
different levels: The \mathematica level where the user provides a
model file, and the C++ level where the generated objects can be
easily exchanged, extended, modified and reused.  This provides great
flexibility for creating custom spectrum generators for both the most
common and most extraordinary models.
